---
title: 'DQ-2: Assignment Week 2'
author: "Jason Grahn"
date: "April 12, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(usethis)

```


#Part 1:  You are estimating the SALES of Tom’s Burger, your client, based on 45 monthly data, the output is as follows:

```{r add standard variables, include=FALSE}
const <- 118.91
betaprice <- 7.908
betaadvert <- 1.863

constSE <- 6.35
priceSE <- 1.096
advertSE <- 0.683

r2 <- 0.448
SSR <- 1718.943
```


Sales=  118.91  - 7.908 Price + 1.863 Advert

(se)    (6.35)    (1.096)       (0.683)

R-sq = 0.448;  
SSR (Residuals) = 1718.943

Note:  In Gretl, Sum of Squares of Residuals is noted as SSR or RSS.

1. What is your interpretation of the coefficient of PRICE?
    * For every positive change of 1 in PRICE, sales will decrease by 7.908.


2. What is your interpretation of the coefficient of ADVERT?
    * For every positive change of 1 in ADVERT, sales will increase by 1.863.


3. What is your interpretation of the coefficient of the Intercept?
    * With no change to PRICE or ADVERT, sales will be approximately 118.91.


```{r predict sales, include=FALSE}
price <- 5.5
advert <- 1200
Sales <- const - (betaprice*price) + (betaadvert*advert)
Sales
```

4. If price is `$5.50` and Advertising expenses are `$1,200`, what is the predicted value of Sales revenue?
    * The predicted value for sales would be `r Sales`.
    
    
```{r question 5 code, include=FALSE}
tconst <- const / constSE
tconst

tprice <- price / priceSE
tprice

tadvert <- advert / advertSE
tadvert

tstat <- 2.2021

tconst > tstat 
tprice > tstat 
tadvert > tstat 

#confidence intervals. the 95% confidence interval is defined as (beta - Tstat * SE) and (beta + Tstat * SE)
betaprice - (tstat*priceSE)
betaprice + (tstat*priceSE)

betaadvert - (tstat*advertSE)
betaadvert + (tstat*advertSE)
```    
5. Conduct t-test for all variables using 95% confidence intervals, state your conclusion.
    * With 45 units in the sample, the closest t-test statistic is for `n=40`, which is `2.021` at `.05 alpha`. The T-stat for constant is: `r tconst`; T-stat for price is: `r tprice`; T-stat for advert is: `r tadvert`. The constant and each variable each test greater than than the t-statistic at `.05 alpha`. The constant and each variable are all statistically significant for the model. The 95% confidence interval for Beta-Price is (`r betaprice - (tstat*priceSE)`, `r betaprice + (tstat*priceSE)`). The The 95% confidence interval for Beta-Advert is (`r betaadvert - (tstat*advertSE)`, `r betaadvert + (tstat*advertSE)`).

```{r question 6 code ftest, include=FALSE}
# r2 = SSR 
    # /TSS    
# so TSS = SSR / r2

TSS <- SSR / r2
TSS

ESS <- TSS - SSR
ESS

#f-tests are goodness of fit for the model and defined as 

(MST <- TSS / 2 - 1)
(MSE <- ESS / 45 - 2)
(Fstat <- MST / MSE)

```
6. Conduct F-test (using R2 to find SST; and find the F-value), state your conclusion
    * With numerator degrees of freedom: 1 and denominator degrees of freedom: 43; The F-test number is `7.31`. The F-statistic generated from `MST / MSE` gives us `r Fstat`. Because the F-statistic is higher than the F-test, we conclude that the model is significant and passes as a good fit.

```{r question 7 code, include=FALSE}
(Adjr2 <- 1 - ((ESS / 45 - 2) / (TSS / 45 - 1))
 )
(AIC <- log(ESS / 45) + (2*2 / 45)
  )
(SC <- log(ESS / 45) + ((2 * log(45) / 45))
    )
```
    
7. Calculate the three model selection criteria (Adjusted R-square, AIC, and SIC)
    * Adjusted R-Squared is `r Adjr2`
    * AIC is `r AIC` 
    * SIC is `r SC` ☺ 
    
    
8. In which case, R-square and Adjusted R-square are exactly the same?
    * In this case the two values are _really_ close but they are not exactly the same. R-squared is `r r2` while Adjusted R-squared is `r Adjr2`.
    

# Part II.  Still referring to the IMF Working Paper on Trust and Inequality:

1. Describe the model. What represent the Dependent Variable? What represent the Independent Variable?
    * The most elaborate model uses a variety of factors; just within pages 7 and 8 I found over 20 potential variables for the model. At it's core, the model is attempting to predict how trust changes according to various factors of inequality. 
    * The dependent variable is _TRUST_. This model uses something considered "generalized trust."
    * The independent variable is _INEQUALITY_. Inequality has two components: Inequality of Opportunity and Inequality of Outcomes. 


4. Is it possible for a reversed causal direction?  Explain.
    * Reverse causality means that after a change to trust, inequality would change as well. Given the statements of the paper, I do not think it is possible for reverse causal direction. Page 8 of the paper discussed this briefly when it stated "There is no evidence that inequality increases the demand for greater redistrubution in the United States. In addition, the return to education has no effect on trust..." The statement imples that once mistrust esists, additional education doesn't breed a more trusting environment.  


5. How are each of the variables measured in this model?
    * Trust is measured as "generalized trust" and is measured via survey. 
    * Inequality is measured in a variety of ways throughout this paper. Residual inequality is measured by wages using the ratio of the 90th and 10th percential of personal wage income as inequality at the top and at the bottom. They also use measures of household inequality such as the GINI, poverty rate, poverty gap, and income shares of top percentile groups. 
    

6. Survey: Can you creatively find ways on how it was conducted? Give two examples of questions (made up your own) for the survey.
    * One question could be: "How much do trust people when you first meet them?" with some sort of 1 to 5 score. Another question could be: "I believe people are generally trustworthy." with some sort of 5-scale disagree to agree scaled answer. 
    

7. Now, look at the conclusion, page 21: does it agree or disagree with your initial intuition?
    * "Inequality at the bottom of the distribution lowers and individual's sense of trust in others..." Yes, this agrees with my initial thoughts: poor folks don't trust others, and the American system that lacks strong rebalancing effects perpetuates this distrust.  